Figures and supplemental figures for ecological resilience ms

### 2023-12-23 ms_figures_supp_figs.qmd
refactor all code for main figs to streamline and/or use functions

List of DuckDB tables

@@

@@

# load packages, source functions, set options, make output file, establish DB connection
library(targets)
library(DBI)
library(duckdb)
library(cowplot)
suppressMessages(library(tidyverse))

@@

# Load project functions
source("R/functions.R")
# source("R/fig_functions.R")

@@

con <- DBI::dbConnect(duckdb::duckdb(),
                      dbdir = "data/sim_out.duckdb",
                      read_only = FALSE)
```

@@

# plotting params
x_text_position_parm <- 550 
max_reserve_frac <- 0.5
max_f_fmsy <- 2.5

@@

# A total of 5 (2023/12/20) simulations were run for each paramter set
# This set allows us to determine the number of simulations to use 
# in the contour plots to produce clear contours by picking a random subset of
# simulations up to the full set of simulations

# num_sims_2_avg <- 5

sims_2_use <- 1:5 # sort(sample(1:sim_nums, size = num_sims_2_avg, replace = FALSE))

@@

## Main figures

brf_white_lp_current \<- get_current_exp(table_name = "larval_pool_blue_rockfish_white_135_75")

brf_white_lp_nice \<- get_nice_exp(table_name = "larval_pool_blue_rockfish_white_135_75")

brf_white_lp_current\[\[1\]\]

brf_white_lp_current\[\[2\]\]

brf_white_lp_current\[\[3\]\]

brf_white_lp_nice\[\[1\]\]

brf_white_lp_nice\[\[2\]\]

brf_white_lp_nice\[\[3\]\]

@@

# Set table names to be used to make the main figures

table_name_nd <- "no_dispersal_blue_rockfish_mei_135_75"
table_name_lp <- "larval_pool_blue_rockfish_mei_135_75"
table_name_nd_white <- "no_dispersal_blue_rockfish_white_135_75"
table_name_lp_white <- "larval_pool_blue_rockfish_white_135_75"

@@

brf_mei_nd_current <- get_current_exp(table_name = table_name_nd)
brf_mei_nd_nice <- get_nice_exp(table_name = table_name_nd)

brf_white_nd_current <- get_current_exp(table_name = table_name_nd_white)
brf_white_nd_nice <- get_nice_exp(table_name = table_name_nd_white)

brf_mei_lp_current <- get_current_exp(table_name = table_name_lp)
brf_mei_lp_nice <- get_nice_exp(table_name = table_name_lp)

brf_white_lp_current <- get_current_exp(table_name = table_name_lp_white)
brf_white_lp_nice <- get_nice_exp(table_name = table_name_lp_white)

@@

# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
species_name <- brf_mei_nd_nice[[2]]
brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
                    sim_species_parms[[species_name]][["biom_exp"]]

## Qry 
qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
              sum(number) as abundance,
              sum(yield) as yield,
              FROM '", table_name_nd, 
              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
              ")

F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
                                         fleps_2_fs = spec_fleps_2_fs)
# F_brf_maxes_yield

out_fs <- df_add_fs_out(
  input_df = sim_res_out,
  spec_fleps_2_fs = spec_fleps_2_fs,
  F_maxes_yield = F_brf_maxes_yield,
  waa_g_df = brf_waa_g_df
)
# out_fs

med_yield <- get_median_yield(input_df = out_fs) 
# med_yield

med_biomass <- get_median_biomass(input_df = out_fs)
# med_biomass

out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)

sum_stats_f_frac_df <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
    median_yield = med_yield,
    median_biomass = med_biomass
  )
# sum_stats_f_frac_df

@@

p1 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
  metR::geom_contour_fill(bins = 12) +
  ggtitle(paste0(
        brf_mei_nd_nice[[2]],
        " ",
        brf_mei_nd_nice[[1]],
        " ",
        brf_mei_nd_nice[[3]],
        ":\nTime below mean median biomass "
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

p2 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
  metR::geom_contour_fill(bins = 12) + 
  ggtitle(paste0(
        brf_mei_nd_nice[[2]],
        " ",
        brf_mei_nd_nice[[1]],
        " ",
        brf_mei_nd_nice[[3]],
        ":\nTime below median max yield"
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

@@

ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.png", 
       plot = fig3, 
       height = 10,
       width = 8)
ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.svg", 
       plot = fig3, 
       height = 10,
       width = 8)

@@

# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
species_name <- brf_mei_lp_nice[[2]]
brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
                    sim_species_parms[[species_name]][["biom_exp"]]

## Qry 
qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
              sum(number) as abundance,
              sum(yield) as yield,
              FROM '", table_name_lp, 
              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
              ")

sim_res_out_brf_mei_lp <- dbGetQuery(conn = con, qry)

########### PIPELINING
F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out_brf_mei_lp,
                                         fleps_2_fs = spec_fleps_2_fs)
F_brf_maxes_yield

out_fs <- df_add_fs_out (input_df = sim_res_out_brf_mei_lp,
                         spec_fleps_2_fs = spec_fleps_2_fs,
                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
out_fs

med_biomass <- get_median_biomass(input_df = out_fs)
med_biomass

out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)

@@

p1 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
  metR::geom_contour_fill(bins = 12) +
  ggtitle(paste0(
        brf_mei_lp_nice[[2]],
        " ",
        brf_mei_lp_nice[[1]],
        " ",
        brf_mei_lp_nice[[3]],
        ":\nTime below mean median biomass "
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

p2 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
  metR::geom_contour_fill(bins = 12) + 
  ggtitle(paste0(
        brf_mei_lp_nice[[2]],
        " ",
        brf_mei_lp_nice[[1]],
        " ",
        brf_mei_lp_nice[[3]],
        ":\nTime below median max yield"
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

@@

ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.png", 
       plot = fig4, 
       height = 10,
       width = 8)
ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.svg", 
       plot = fig4, 
       height = 10,
       width = 8)

@@

### Figure 5

Representative timeseries of total population biomass under different combinations of fishing rate and marine reserve protection.

@@

```{r}
#| label: figure_5

bio_yield_df <- out_fs
summary_stats_df <- sum_stats_f_frac_df

yield_thresh <- med_yield
biomass_thresh <- med_biomass

exp_deets <- brf_mei_lp_nice

text <- TRUE
# x_text_val <- 550
x_min <- 1
x_max <- 135
x_text_val <- (x_max) - (x_max - x_min)/2

r_seed <- 34

frac_reserves <- c(0, 0.25, 0.50)
f_fmsys <- c(0.52, 1.00, 2.09)

# facet_bm_yld_ts_plots <- function(bio_yield_df,  # main_plt_df
#                                  summary_stats_df, # sub_plt_df,
#                                  yield_thresh,
#                                  biomass_thresh,
#                                  exp_deets,
#                                  x_text_val = 550,
#                                  r_seed = 34,
#                                  frac_reserves = c(0, 0.25, 0.50),
#                                  f_fmsys = c(0.52, 1.00, 2.09)) {

set.seed(r_seed)
sim_2_use <-
  sample(sort(unique(bio_yield_df$sim_num)), 1, replace = FALSE)

f_fmsys_bio <- c(0, f_fmsys)

### FUNCTION
plt_species <- unique(exp_deets[[2]])
plt_dispersal <- unique(exp_deets[[1]])
plt_noise <- unique(exp_deets[[3]])

title_string <- paste0(
  "Simulation results: \n",
  plt_species,
  " with ",
  plt_dispersal,
  " dispersal and ",
  plt_noise,
  " noise. \n"
)

### FUNCTION
u_f_fmsys <- unique(bio_yield_df$f_fmsy)

u_f_fmsys <-
  purrr::map_dbl(f_fmsys_bio,  ~ u_f_fmsys[which.min(abs(u_f_fmsys - .x))])

### FUNCTION
bio_yield_sel_df <- bio_yield_df %>%
  dplyr::mutate(reserve_frac = as.numeric(reserve_frac),
                year = year - 500) %>%
  dplyr::filter(sim_num == sim_2_use) %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = reserve_frac, tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`)) %>%
  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
  dplyr::summarize(annual_biomass = sum(biomass_at_age),
                   annual_yield = sum(yield),
                   rel_annual_biomass = sum(biomass_at_age) / med_biomass,
                   rel_annual_yield = sum(yield) / med_yield) %>%
  dplyr::ungroup()

### Biomass
biom_ts_plt <- ggplot(
  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
  aes(x = year, y = rel_annual_biomass)
  # aes(x = year, y = annual_biomass)
) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  # geom_ribbon(aes(
  #   ymin = biomass_thresh,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass lower"
  # )) +
    geom_ribbon(aes(
    ymin = 1,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass lower"
  )) +
  # geom_ribbon(aes(
  #   ymin = annual_biomass,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass higher"
  # )) +
    geom_ribbon(aes(
    ymin = rel_annual_biomass,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass higher"
  )) +
  geom_line(colour = "black") +
    geom_segment(aes(x = 1, y = 1, 
                     xend = 135, yend = 1),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 11000,
  #   aes(label = mean_biomass_lab)
  # ) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 12500,
  #   aes(label = sd_biomass_lab)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 14000,
#   aes(label = yrs_below_thresh)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 9500,
#   aes(label = cv_biomass_lab)
# ) +
labs(fill = "Above/Below Biomass threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  # ylab("Biomass (metric tons)") +
  ylab("Relative Biomass") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_bw() +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white")#,
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.border = element_blank()
  )

#### Yield
yld_ts_plt <- bio_yield_sel_df %>%
  dplyr::filter(f_fmsy != 0) %>%
  ggplot(data = ., aes(x = year, y = rel_annual_yield)) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  geom_ribbon(aes(
    ymin = 1,
    ymax = pmin(rel_annual_yield, 1),
    fill = "Yield lower"
  )) +
  geom_ribbon(aes(
    ymin = rel_annual_yield,
    ymax = pmin(rel_annual_yield, 1),
    fill = "Yield higher"
  )) +
  geom_line(colour = "black") +
  geom_segment(aes(x = 1, y = 1, 
                     xend = 135, yend = 1),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 11000,
  #   aes(label = mean_biomass_lab)
  # ) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 12500,
  #   aes(label = sd_biomass_lab)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 14000,
#   aes(label = yrs_below_thresh)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 9500,
#   aes(label = cv_biomass_lab)
# ) +
labs(fill = "Above/Below Yield threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  # ylab("Yield (metric tons)") +
  ylab("Relative Yield") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_bw() +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white")#,
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.border = element_blank()
  )
# }

print(biom_ts_plt)
print(yld_ts_plt)

ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries.png", plot = biom_ts_plt,
       height = 8, width = 10)
ggsave(filename = "output/tmp_figs/fig6-yield-timeseries.png", plot = yld_ts_plt,
       height = 8, width = 10)

ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries.svg", plot = biom_ts_plt,
       height = 8, width = 10)
ggsave(filename = "output/tmp_figs/fig6-yield-timeseries.svg", plot = yld_ts_plt,
       height = 8, width = 10)

@@

```{r}
### Biomass

summary_stats_df_plot <- summary_stats_df[[2]] %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`))

summary_stats_df_plot_yld <- summary_stats_df[[2]] %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys[-1], near, x = f_fmsy, tol = 1e-4
  ), `|`))

biom_ts_plt <- ggplot(
  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
  aes(x = year, y = rel_annual_biomass)
  # aes(x = year, y = annual_biomass)
) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  # geom_ribbon(aes(
  #   ymin = biomass_thresh,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass lower"
  # )) +
    geom_ribbon(aes(
    ymin = 1,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass lower"
  )) +
  # geom_ribbon(aes(
  #   ymin = annual_biomass,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass higher"
  # )) +
    geom_ribbon(aes(
    ymin = rel_annual_biomass,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass higher"
  )) +
  geom_line(colour = "black") +
    geom_segment(aes(x = 1, y = 1, 
                     xend = 135, yend = 1),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 11000,
  # aes(label = mean_biomass_lab)
  y = 3.4,
  size = 3,
  aes(label = mean_rel_biomass_lab)
) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 12500,
  # aes(label = sd_biomass_lab)
  y = 3.1,
  size = 3,
  aes(label = sd_rel_biomass_lab)
) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 14000,
  # aes(label = yrs_below_thresh)
  y = 2.8,
  size = 3,
  aes(label = yrs_below_biomass_thresh_lab)
) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 9500,
  # aes(label = cv_biomass_lab)  
  y = 2.5,
  size = 3,
  aes(label = cv_rel_biomass_lab)
) +
labs(fill = "Above/Below Biomass threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  # ylab("Biomass (metric tons)") +
  ylab("Relative Biomass") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_bw() +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white")#,
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.border = element_blank()
  )

#### Yield
# summary_stats_df_plot_yld

>>>>

List of tables in "data/sim_out.duckdb":

@@

This .rmd file can be run as a script that produces the main text figues and the supporting figures for the manuscript *Marine reserves can provide buffering against environmental fluctuations to overexploited but not sustainably harvested fisheries*.

In RStudio, click on `Code` -\> `Run Region` --\> `Run All` to run the script and create all the files.

To render an .html file from RStudio, click the Render button.

To export to pdf, follow the instructions [here](https://quarto.org/docs/output-formats/pdf-basics.html) to install a Quarto "friendly" Tex distribution. Then click the small down arrow of the Render button and select `Render as pdf`

Exporting to a Word (.docx) file requires that MS Word/Office is installed, then click the small down arrow of the Render button and select `Render as MS Word` .

@@

# load packages, source functions, set options, make output file, establish DB connection
library(targets)
suppressMessages(library(tidyverse))
library(cowplot)
library(DBI)
library(duckdb)

@@

# Load project functions
source("R/functions.R")

@@

@@

# plotting params
max_reserve_frac <- 0.5
max_f_fmsy <- 2.5

@@

# A total of `sim_nums` simulations were run for each paramter set.
# Running multiple simulations helps to produce clear contours and reduce
# impact of artifacts of a single simulation run

sims_2_use <- 1:sim_nums

@@

## Main text figures

@@

# Set table names to be used to make the main figures for blue rockfish

table_name_brf_nd_mei <- "no_dispersal_blue_rockfish_mei_135_75"
table_name_brf_lp_mei <- "larval_pool_blue_rockfish_mei_135_75"
table_name_brf_nd_white <- "no_dispersal_blue_rockfish_white_135_75"
table_name_brf_lp_white <- "larval_pool_blue_rockfish_white_135_75"

@@

brf_nd_mei_current <- get_current_exp(table_name = table_name_brf_nd_mei)
brf_nd_mei_nice <- get_nice_exp(table_name = table_name_brf_nd_mei)

brf_nd_white_current <- get_current_exp(table_name = table_name_brf_nd_white)
brf_nd_white_nice <- get_nice_exp(table_name = table_name_brf_nd_white)

brf_lp_mei_current <- get_current_exp(table_name = table_name_brf_lp_mei)
brf_lp_mei_nice <- get_nice_exp(table_name = table_name_brf_lp_mei)

brf_lp_white_current <- get_current_exp(table_name = table_name_brf_lp_white)
brf_lp_white_nice <- get_nice_exp(table_name = table_name_brf_lp_white)

## Blue rockfish reproductive biology and fishery params

# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
species_name <- brf_nd_mei_nice[[2]]
brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
                    sim_species_parms[[species_name]][["biom_exp"]]

# use functions to create useful data structures
# FLEP to F reference tables by species
spec_fleps_2_fs_brf <-
  get_fs_from_fleps(species = species_name,
                    flep_inds = species_flep_fished_ind,
                    f_vals =  fishing_mortality_values)

@@

sim_res_out_brf_nd_mei <-
  qry_get_sim_data_for_analysis(table_name = table_name_brf_nd_mei)
# sim_res_out_brf_nd_mei

F_brf_maxes_yield_brf_nd_mei <- get_f_maxes_yield(input_df = sim_res_out_brf_nd_mei,
                                         fleps_2_fs = spec_fleps_2_fs_brf)
# F_brf_maxes_yield_brf_nd_mei

out_fs_brf_nd_mei <- df_add_fs_out(
  input_df = sim_res_out_brf_nd_mei,
  spec_fleps_2_fs = spec_fleps_2_fs_brf,
  F_maxes_yield = F_brf_maxes_yield_brf_nd_mei,
  waa_g_df = brf_waa_g_df
)
# out_fs_brf_nd_mei

med_yield_brf <- get_median_yield(input_df = out_fs_brf_nd_mei) 
# med_yield_brf

med_biomass_brf <- get_median_biomass(input_df = out_fs_brf_nd_mei)
# med_biomass__brf_nd_mei

out_yld_bm_sims_f_frac_yr_brf_nd_mei <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_nd_mei)
# out_yld_bm_sims_f_frac_yr_brf_nd_mei

sum_stats_f_frac_df_brf_nd_mei <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_nd_mei,
    median_yield = med_yield_brf,
    median_biomass = med_biomass_brf
  )
# sum_stats_f_frac_df_brf_nd_mei

@@

p1 <-
  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_mei,
                               spec_disp_noise = brf_nd_mei_nice)

p2 <-
  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_mei,
                                spec_disp_noise = brf_nd_mei_nice)

@@

print(fig3)

ggsave(filename = "output/main_figs/fig3-brf-nd-mei-biomass-yield.png",
       plot = fig3,
       height = 10,
       width = 8)
ggsave(filename = "output/main_figs/fig3-brf-nd-mei-biomass-yield.svg",
       plot = fig3,
       height = 10,
       width = 8)

@@

# # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
# species_name <- brf_mei_lp_nice[[2]]
# brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
#                     sim_species_parms[[species_name]][["biom_exp"]]
# 
# brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
#                            waa_g = brf_waa_g)
# 
# # use functions to create useful data structures
# # FLEP to F reference tables by species
# spec_fleps_2_fs <-
#   get_fs_from_fleps(species = species_name,
#                     flep_inds = species_flep_fished_ind,
#                     f_vals =  fishing_mortality_values)

sim_res_out_brf_lp_mei <-
  qry_get_sim_data_for_analysis(table_name = table_name_brf_lp_mei)

F_brf_maxes_yield_brf_lp_mei <- get_f_maxes_yield(input_df = sim_res_out_brf_lp_mei,
                                         fleps_2_fs = spec_fleps_2_fs_brf)
# F_brf_maxes_yield_brf_lp_mei

out_fs_brf_lp_mei <- df_add_fs_out (input_df = sim_res_out_brf_lp_mei,
                         spec_fleps_2_fs = spec_fleps_2_fs_brf,
                         F_maxes_yield = F_brf_maxes_yield_brf_lp_mei, 
                         waa_g_df = brf_waa_g_df)
# out_fs_brf_lp_mei

out_yld_bm_sims_f_frac_yr_brf_lp_mei <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_lp_mei)
# out_yld_bm_sims_f_frac_yr_brf_lp_mei

sum_stats_f_frac_df_brf_lp_mei <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_lp_mei,
    median_yield = med_yield_brf,
    median_biomass = med_biomass_brf
  )
# sum_stats_f_frac_df_brf_lp_mei

@@

p1 <-
  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_mei,
                               spec_disp_noise = brf_lp_mei_nice)

p2 <-
  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_mei,
                                spec_disp_noise = brf_lp_mei_nice)

@@

print(fig4)

ggsave(
  filename = "output/main_figs/fig4-brf-lp-mei-biomass-yield.png",
  plot = fig4,
  height = 10,
  width = 8
)
ggsave(
  filename = "output/main_figs/fig4-brf-lp-mei-biomass-yield.svg",
  plot = fig4,
  height = 10,
  width = 8
)

@@

### Figure 5 and 6

Representative timeseries of total population biomass and yield ( under different combinations of fishing rate and marine reserve protection.

@@

```{r}
#| label: figure_5_6

biom_ts_plt <- facet_plot_bm_ts_plots(
  bio_yield_df = out_fs_brf_lp_mei,
  biomass_thresh = med_biomass_brf,
  yield_thresh = med_yield_brf,
  exp_deets = brf_lp_mei_nice,
  r_seed = 34,
  frac_reserves = c(0, 0.25, 0.50),
  f_fmsys = c(0, 0.5, 1.00, 2.)
)

yield_ts_plt <- facet_plot_yld_ts_plots(
  bio_yield_df = out_fs_brf_lp_mei,
  biomass_thresh = med_biomass_brf,
  yield_thresh = med_yield_brf,
  exp_deets = brf_lp_mei_nice,
  r_seed = 34,
  frac_reserves = c(0, 0.25, 0.50),
  f_fmsys = c(0.5, 1.00, 2.)
)

print(yield_ts_plt)

print(biom_ts_plt)

ggsave(filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei.png", plot = biom_ts_plt,
       height = 8, width = 10)
ggsave(filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei.svg", plot = biom_ts_plt,
       height = 8, width = 10)

ggsave(filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei.png", plot = yield_ts_plt,
       height = 8, width = 10)
ggsave(filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei.svg", plot = yield_ts_plt,
       height = 8, width = 10)

@@

```{r}
#| label: fig_5_text
### Biomass

frac_reserves <- c(0, 0.25, 0.5)
f_fmsys <- c(0, 0.5, 1.00, 2)

u_f_fmsys <- unique(sum_stats_f_frac_df_brf_lp_mei[[2]]$f_fmsy)

  u_f_fmsys <-
    purrr::map_dbl(f_fmsys,  ~ u_f_fmsys[which.min(abs(u_f_fmsys - .x))])

summary_stats_df_plot_bm <- sum_stats_f_frac_df_brf_lp_mei[[2]] %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`))

summary_stats_df_plot_yld <- sum_stats_f_frac_df_brf_lp_mei[[2]] %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys[-1], near, x = f_fmsy, tol = 1e-4
  ), `|`))

# Location to place text
x_text_val <- 135/2

biom_ts_plt <- biom_ts_plt +
  geom_text(
    data = summary_stats_df_plot_bm,
    x = x_text_val,
    y = 3.4,
    size = 3,
    aes(label = mean_rel_biomass_lab)
  ) +
  geom_text(
    data = summary_stats_df_plot_bm,
    x = x_text_val,
    y = 3.1,
    size = 3,
    aes(label = sd_rel_biomass_lab)
  ) +
  geom_text(
    data = summary_stats_df_plot_bm,
    x = x_text_val,
    y = 2.8,
    size = 3,
    aes(label = cv_rel_biomass_lab)
  ) +
  geom_text(
    data = summary_stats_df_plot_bm,
    x = x_text_val,
    y = 2.5,
    size = 3,
    aes(label = yrs_below_biomass_thresh_lab)
  )

print(biom_ts_plt)

ggsave(
  filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei-text.png",
  plot = biom_ts_plt,
  height = 8,
  width = 14
)
ggsave(
  filename = "output/main_figs/fig5-biomass-timeseries-brf-lp-mei-text.svg",
  plot = biom_ts_plt,
  height = 8,
  width = 14
)

### Figure 6 with text

```{r}
#| label: figure_6_text

# Yield

yield_ts_plt <- yield_ts_plt +
  geom_text(
    data = summary_stats_df_plot_yld,
    x = x_text_val,
    y = 1.9,
    size = 2,
    aes(label = mean_rel_yield_lab)
  ) +
  geom_text(
    data = summary_stats_df_plot_yld,
    x = x_text_val,
    y = 1.8,
    size = 2,
    aes(label = sd_rel_yield_lab)
  ) +
  geom_text(
    data = summary_stats_df_plot_yld,
    x = x_text_val,
    y = 1.7,
    size = 2,
    aes(label = cv_rel_yield_lab)
  ) +
  geom_text(
    data = summary_stats_df_plot_yld,
    x = x_text_val,
    y = 1.6,
    size = 2,
    aes(label = yrs_below_yield_thresh_lab)
  )

print(yield_ts_plt)

ggsave(
  filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei-text.png",
  plot = yield_ts_plt,
  height = 8,
  width = 14
)
ggsave(
  filename = "output/main_figs/fig6-yield-timeseries-brf-lp-mei-text.svg",
  plot = yield_ts_plt,
  height = 8,
  width = 14
)
